%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{awesome-cv}
\fontdir[fonts/] % override a directory location for fonts(default: 'fonts/')
% \newcommand*{\sectiondir}{resume/} % Configure a directory location for sections

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}

%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]

%\usepackage{import} % Needed to divide into several files


% Header --------------------------------------------------------------------------------------------

\begin{document}

\begin{center}
\headerlastnamestyle{Keith F. Ma}
\vspace{0.4mm}

\headeraddressstyle{keithfma@gmail.com}
\enskip\textbar\enskip
\headeraddressstyle{610-389-1406}
\enskip\textbar\enskip
\headeraddressstyle{Hanover, NH}
\enskip\textbar\enskip
\headeraddressstyle{\href{http://github.com/keithfma}{github.com/keithfma}}
\enskip\textbar\enskip
\headeraddressstyle{\href{http://linkedin.com/in/keithfma}{linkedin.com/in/keithfma}}

\descriptionstyle{Software engineer with 10 years experience translating cutting-edge research into practical software and a strong background in science and ML. Looking to build tools that make hard tasks easy and the world a better place.}


\end{center}
  
% body -------------------------------------------------------------------------------------------------

% TODO: Reconsider tools section. Liz suggests another category separating sci from "devops". The reason was that
%   it feels like a "grab bag" without focus. 

% TODO: Double-check capitalization for languages, etc.

\cvsection{Skills}
\begin{cvskills}
\cvskill{Languages}{Python, Javascript,C, Fortran, Shell, SQL, MATLAB}
\cvskill{Tools}{AWS, Airflow, PostGIS, Docker, CircleCI, GDAL/OGR, scipy, SQLAlchemy, celery, flask}
\end{cvskills}

\cvsection{Experience}
\begin{cventries}

  \cventrydouble
    {Indigo Ag}  % org
    {Boston, MA}  % location 
    {Staff Software Engineer}  % most recent title
    {March 2023 - Present}  % most recent dates
    {
    \begin{cvitems}
      \item Led engineering for life cycle analysis library that applies input-output modeling to estimate cash crop CO\textsubscript{2} emissions from farmer actions and materials used. Includes a novel method for preprocessing model uncertainty that is currently in the patent application process.
      \item Improved team performance and built internal alignment by mentoring junior engineers, sharing knowledge with peers, and collaborating with science and product teams on requirements, milestones, and prioritization.
    \end{cvitems}
    }
    {Senior Software Engineer}  % previous title
    {Jan. 2019 - March 2023}  % previous title dates
    {
    \begin{cvitems}
      \item Developed data remediation service for a system that estimates soil organic carbon over time for >10k fields in the US, leading to >130k tons CO\textsubscript{2} sequestered so far \link{https://patents.google.com/patent/US20240020775A1}{(patent)}. Integrates ML inferences, statistical reports, and subject matter expertise to identify missing/erroneous data and patch it with scientifically-defensible synthetic data. Designed and tested in collaboration with science and policy teams.
      \item Built tools for satellite imagery visualization and analysis, including field boundary detection \link{https://patents.google.com/patent/US20220180526A1}{(patent)} and an on-demand image tiling service for interactive visualization of the latest 20m/pixel resolution imagery in Indigo’s web applications with a 100ms response time \link{https://patents.google.com/patent/US20230092057A1}{(patent)}.
    \end{cvitems}
    }

  \cventrytight
    {Software Engineer}
    {TellusLabs (acquired by Indigo Ag)}
    {Somerville, MA}
    {Aug. 2018 - Jan. 2019}
    {
    \begin{cvitems}
      \item Core developer for a global satellite analytics platform predicting agricultural yields from field- to national-scale
    \end{cvitems}
    }

  \cventrytight
    {Data Science Fellow}
    {Insight Data Science}
    {Boston, MA}
    {June 2018 - Present}
    {
    \begin{cvitems}
      \item Built an MVP \link{https://www.allnans.com/jekyll/update/2018/08/07/introducing-parasol.html}{navigation app} that optimizes for comfortable outdoor travel in sun or shade by simulating sunlight along potential routes from dense LiDAR points and the OpenStreetMap graph
    \end{cvitems}
    }

  \cventrytight
    {Research Scientist}
    {Boston Fusion Corp}
    {Lexington, MA}
    {June 2016 - May 2018}
    {
      \begin{cvitems}
        \item Created ML-based analytical tools to address a wide range of Department of Defense needs, including adaptive decision support systems, data exploration via multi-level graphs, and AI for interactive training games
      \end{cvitems}
    }

  \cventrytight
    {Scientific Programmer / Analyst}
    {Boston University Research Computing Services}
    {Boston, MA}
    {Sept. 2014 - June 2016}
    {
      \begin{cvitems}
        \item {Consulted with faculty and students to optimize and parallelize research software for an \link{https://www.bu.edu/tech/support/research/computing-resources/scc}{18k core computing cluster}} 
      \end{cvitems}
    }

  \cventrytight
    {Doctoral Candidate}
    {Yale University Department of Geology \& Geophysics}
    {New Haven, CT}
    {Sept. 2007 - Sept. 2014}
    {
      \begin{cvitems}
        \item {Designed and built a distributed numerical model to simulate erosion by rivers and glaciers}
        \item {Created a method for reconstructing past topography by decomposing and scaling modern topographic features}
        \item {Built a physical model of mountain formation and software for measuring velocity fields from experiment imagery}
      \end{cvitems} 
    }

\end{cventries}

% cludge to force things onto this page
\vspace{-1em}

\cvsection{Education}
\begin{cventries}
  \cventry
    {M.Phil in Geology \& Geophysics}
    {Yale University}
    {New Haven, CT}
    {Dec. 2009}
    {}
  \cventry
    {BA in Geology - Biology}
    {Brown University}
    {Providence RI}
    {May 2005}
    {}
\end{cventries}

\end{document}
